---
title: "Anova"
author: "Washim Ahmed"
date: "12/25/2016"
output: pdf_document
---

```{r, echo=TRUE}
library(readxl)
library(tidyverse)
age_of_workers <- read_excel("~/manipal_practice/anova.xls")
summary(age_of_workers)
combine_all_ages <- gather(age_of_workers, "Factory", "Age", 1:3)
anova <- aov(formula = Age ~ Factory, data = combine_all_ages)
summary(anova)
```

I can see p value is **very very tiny** which is less than significance value of 0.01 (0.01 given in assignment) therefore I can **reject null hypothesis** which means there is a **significant age difference across factories**.

I will do **TukeyHSD** test to identify which factory workers does have significance age difference.

```{r, echo=TRUE}
TukeyHSD <- TukeyHSD(anova)
TukeyHSD
plot(TukeyHSD)
```

1. For Tamil Nadu and Himachal Pradesh where P value 0 < 0.01 which means Tamil Naru's workers are older than Himachal Pradesh
2. For Uttarakhand and Tamil Nadu where P value 0 < 0.01 which means Tamil Naru's workers are older than Uttarakhand

**The workers at Tamil Naru factory are older than the ones at the other factories.**














