---
title: "HackerRank Assignments"
author: "Washim Ahmed"
date: "2/17/2017"
output: pdf_document
number_sections: true
toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Laptop Battery Life

## Problem Statement

How long Fred will be able to watch TV with giver charge.

## Solutions

To solve this I will do following test with current dataset.

1. **Corelations Plot**

2. **Linear regression**

Using above analysis I belive I can predict how long battery will last.

### Corelation Plot
```{r, fig.height=3}
library(graphics)
batery <- read.csv("https://s3.amazonaws.com/hr-testcases/399/assets/trainingdata.txt")
colnames(batery) <- c("charged","lasted")
plot(batery$charged,batery$lasted)
```

**It was clear from graph that charger charged <= 4 hours have 100% corelation and > 4 hours battery will last always 8 hours.**

### Linear regression

This problem statement not at all required linear regression because it was clear from above graph that charger charged <= 4 hours have 100% corelation and > 4 hours battery will last always 8 hours.


## Hacker Rank R code
```{r, eval=FALSE, include=TRUE}
# Hacker rank submission link https://www.hackerrank.com/challenges/battery/submissions/code/38404203
input <- readLines('stdin', n=1, warn=FALSE)
input <- as.numeric(input)
write(ifelse(input > 4, 8, input * 2),stdout())
```

## Competition Score

I had scored 10 out of 10 in hacker rank.

## Conclusion
Fred 4 hours charging is enough for you to get better performance because more than 4 hours charging does not increase any performance.

# Predicting House Prices

## Problem Statement

Estimate house price per square feet for Charlie.

## Solutions

Its clearly linear regression problem with multiple features.


## Hacker Rank R code

```{r, eval=FALSE, include=TRUE}
# Hacker rank submission link https://www.hackerrank.com/challenges/predicting-house-prices/submissions/code/38472023
rawinput <- read.table("stdin",fill = TRUE, header = FALSE)
row <- as.numeric(rawinput[1,2])
train <- rawinput[2:(row+1),]
train <- as.data.frame(train)
colnames(train)[3] <- "Price"
test <- rawinput[(row+3):nrow(rawinput),c(1,2)]
test <- as.data.frame(test)
fit <- lm(Price ~ V1 + V2, data = train)
output <- round(predict(fit, test), digits = 2)
write(output,stdout(), sep = "\n")
```

## Sample Input

2 7

0.18 0.89 109.85

1.0 0.26 155.72

0.92 0.11 137.66

0.07 0.37 76.17

0.85 0.16 139.75

0.99 0.41 162.6

0.87 0.47 151.77

4

0.49 0.18

0.57 0.83

0.56 0.64

0.76 0.18

## Sample Output

105.22

142.68

132.94

129.71













