---
title: "Exploratory Data Analysis Clustering"
author: "Washim Ahmed"
date: "12/20/2016"
output: pdf_document
---

## Assignment 1 (A)
Write the R Program for the following steps.

**(a)Load mtcars() dataframe**

```{r echo=TRUE}
my_cars <- mtcars
head(my_cars)
```

**(b) Add a column name qualCat, a new column which takes the value of A if mpg  < 15 and B if mpg >=15**

```{r echo=TRUE}
library(dplyr)
my_cars <- my_cars %>%
  mutate(qualCat = ifelse(mpg >= 15, "B", "A"))
head(my_cars,50)
```

**(c) Save this data frame locally**

```{r my_cars, echo=TRUE}
write.csv(my_cars, file = "~/manipal_practice/mycars.csv") # Given my Unix system path
```

**(d)Load this file on to RStudio and know the different types of variables**

```{r mtcars}
mycars <- read.csv("~/manipal_practice/mycars.csv")
str(mycars) # Display structure of variables with observations
summary(mycars) # Display summary
colnames(mycars) # Display Columns
dim(mycars) # Display total observations and total variables
```

## Assignment 1 (B)
Write an R program for clustering the drinks.csv file using k-means clustering. 

```{r, echo=TRUE}
library(factoextra)
drinks <- read.csv(file = "~/manipal_practice/drinks.csv")
drinks <- na.omit(drinks)
set.seed(786)
cluster <- kmeans(drinks[-1], centers = 3)
fviz_cluster(cluster, data = drinks[-1], geom = "point", stand = FALSE)
```

**Also use the elbow method to infer the optimal value of K**

```{r, echo=TRUE}
library(ggplot2)
drinks <- data.matrix(drinks)
maxk <- 15
wssdist <- sapply(1:maxk, function(y){
  k <- kmeans(drinks[-1], y, nstart = 10)
  return(k$tot.withinss)
})

distdf <- data.frame(cluster = 1:maxk, wssdist = wssdist)

g <- ggplot(data = distdf, aes(x = cluster, y = wssdist))
g <- g + geom_line(aes(color = "tot.withinss")) + geom_point()
g <- g + geom_vline(xintercept = 3, linetype = "dashed")
g <- g + ylab("Within groups sum of squares") + xlab("Number of Clusters")
g <- g + ggtitle("Elbow method to infer the optimal value of K")
g <- g + scale_x_continuous(breaks = 1:maxk)
g
```

### **Optimal value of K is 3**










